### 2021-07-09 doc/thesis/chapters/system-architecture-and-concept.tex
optional floating images
generate new
rename diagrams
system level overview detailed bd

@@

%%%%%%%%%%%%%%%%%%%%
\section{Block Diagram}

>>>>

\noindent
A very high-level overview of the entire system is given the block diagram in Fig.\ref{fig:bd_system_overview_highlevel}.

\includepicture [1.0] [0] [H] {High-level overview of the system.} {bd_system_overview_highlevel} {img/draw.io/bd_system_overview_highlevel}

@@

%%%%%%%%%%%%%%%%%%%%
\section{System concept}

\includepicture [1.0] [0] [H] {Block diagram of the overall system concept.} {bd_system_overview_detailed} {img/draw.io/bd_system_overview_detailed}
